Seismic parameter estimation and the Canadian crust

### 2013-07-04 paper/draftBP.tex
paper

\subsection{Regional Bulk Crustal Parameters}
[[ Are we using ZK + semblance, or Full Grid Search + semblance ]]
  Data from X seismic stations across Canada are analyzed, using only those stations with less than 0.06 standard error.

@@

\subsection{Slave Province}
<Discussion on Slave Province>

%% -----------------------------------------------%%
\section{Conclusions}
<Conclusions here>

>>>>

\subsection{Regional Bulk Crustal Parameters}
[[ Move from ZK + semblance to Full Grid Search + semblance ]]
  Data from X seismic stations across Canada are analyzed, using only those stations with less than 0.06 standard error. To compensate for the uneven geographic distribution of seismic stations, weights are applied to all crustal parameter estimates before averaging over a given region. Wieghts are calculated by first projecting station locations onto the 2D plane using the Albers equal-area conic projection. A Voronoi diagram is calculated for all projected station locations. The ratio between the Voronoi cell surface encompassing each station and the total area of the convex hull bounding region is computed and used as the weighting value.

\begin{table}
  \begin{tabular}{ l l l l l l }
    \cline{2-6}
    & \multicolumn{2}{ c }{ZK + semblance} & \multicolumn{2}{ c }{Crust 2.0} & \multicolumn{1}{ c }{Active Source} \\
    \hline
    Region & $R$ & $H [km]$ & $R$ & $H [km]$ & $V_P [km/s]$ \\
    \hline
    Canada     & 37.0 & 1.75 & 38.2 & 1.77 & 6.33\\
    Shield     & 39.2 & 1.74 & 38.8 & 1.77 & 6.42\\
    Slave      & 38.2 & 1.74 & 37.0 & 1.76 & 6.44\\
    Churchill  & 38.9 & 1.73 & 37.8 & 1.77 & 6.39\\
    Superior   & 39.7 & 1.74 & 39.1 & 1.76 & 6.44\\
    Grenville  & 41.7 & 1.78 & 40.5 & 1.78 & 6.48\\
    \hline
  \end{tabular}
  \caption{Comparison of $R$ and $H$ estimates with three published studies}
\label{table:regionParameters}

  Moving South from the Churchill through the Superior and the Grenville there is an increase in the ZK + semblance computed seismic velocity ratio as well as crustal thickness. The trend in increasing values is also seen in the weighted averaged active source $V_P$ data. Generally the Crust 2.0 values show a slightly thinner crust though the southward thickening trend is noticeble. The trend in the seismic velocity data is not as apparent in the Crust 2.0 data.

@@

%% -----------------------------------------------%%
\section{Conclusions}
Conclusions here
